Backpropagating Gravitational wave events

### 2022-03-10 src/ms.tex
Update zenodo dependecies
Add result paragraph

% \begin{figure*}
% \includegraphics[width=0.98\textwidth]{GW150914_corner.pdf}
% \caption{The posterior for GW150914}
% \label{fig:GW150914_posterior}
% \end{figure*}

% \begin{figure}
% \includegraphics[width=0.49\textwidth]{GW150914_reprojection.pdf}
% \caption{Reprojecting the posterior in evolutionary parameter space of GW150914 to observable space.}
% \label{fig:GW150914_reprojection}
% \end{figure}

@@

@@

We hope this letter would motivate the community to build the relevant infrastructure mentioned above,
so in the near future we can explore the full parameter space of binary evolution models with the next-generation GW detectors network.
Interpretation:
\begin{enumerate}
\item Highlight the fact that we turn hyper-parameters into parameters.
\item Discuss this is need for high dimensional exploration.
\end{enumerate}

>>>>

We show our main result in figure \ref{fig:GW150914_posterior}. 
\kw{Recover ratio of the posterior sample goes here.}

\begin{figure*}
\includegraphics[width=0.98\textwidth]{static/GW150914_corner.pdf}
\caption{The posterior for GW150914 in both the progenitor parameter space and hyper-parameter space.
$M_1$ and $M_2$ are the progenitors' masses. $\log{t_{orb}}, e, \log{Z}$ are the progenitor binary's log orbital period, eccentricity and log metallicity at ZAMS.
$\alpha$ is the common envelope efficiency.
$f_{\rm acc}$ is the fraction of mass accreted during stable mass transfer.
$q_{\rm crit 3,4}$ are the ciritical mass during \kw{Katie fill in},
$\sigma$ is the mean magnitude of the Maxwellian distribution characterizing natal kick strength.
}
\label{fig:GW150914_posterior}
\end{figure*}

To check the validity of the recovered posterior, it is essential to check whether it is consistent with the original posterior in the observable space.
We reproject the recovered posterior to the observable space, and compare the KL divergence between the original posterior and the reprojected posterior.
For GW150914, the KL divergence between the reprojected posterior and the original posterior is \kw{fill later} on average.
The KL divergence stays stable for reprojecting with different random seeds.

\begin{figure}
\includegraphics[width=0.49\textwidth]{static/GW150914_reprojection.pdf}
\caption{Reprojecting the posterior in evolutionary parameter space of GW150914 to observable space.
The blue contour is the posterior reprojected using the samples in the evolutionary parameter space.
The orange contour is the posterior samples from LVK that have corresponding samples in the evolutionary parameter space.
The green contour is the posterior plotted using all of LVK posterior samples.
}
\label{fig:GW150914_reprojection}
\end{figure}

@@

\kw{Add figure of stable mass transfer vs common envelope}

@@

We hope this letter would motivate the community to build the relevant infrastructure mentioned above,
so in the near future we can explore the full parameter space of binary evolution models with the next-generation GW detectors network.

Interpretation:
\begin{enumerate}
\item Highlight the fact that we turn hyper-parameters into parameters.
\item Discuss this is need for high dimensional exploration.
\end{enumerate}
